### 2018-08-21 pilot_manuscript.Rmd
fixed the graph

long_mlm$moraltype = factor(long_mlm$moraltype, 
                  levels=c("hperhi", "hperlo", "fperhi", "fperlo",
                           "iperhi", "iperlo", "aperhi", "aperlo", "pperhi", "pperlo"),
                  labels = c("Harm-positive", "Harm-negative", "Fair-positive",
                             "Fair-negative", "Ingroup-positive", "Ingroup-negative",
                             "Authority-positive", "Authority-negative", 
                             "Purity-positive", "Purity-negative")) 
cleanup = theme(panel.grid.major = element_blank(), 
                panel.grid.minor = element_blank(), 
                panel.background = element_blank(), 
                axis.line.x = element_line(color = "black"),
                axis.line.y = element_line(color = "black"),
                legend.key = element_rect(fill = "white"),
                text = element_text(size = 15))
overallgraph = ggplot(long_mlm, aes(moraltype, percent, fill = lean))
overallgraph +
  stat_summary(fun.y = mean,
               geom = "bar",
               position = "dodge") +
  stat_summary(fun.data = mean_cl_normal,
               geom = "errorbar", 
               position = position_dodge(width = 0.90),
               width = .2) +
  xlab("Moral Category") +
  ylab("Percent") + 
  cleanup +
  scale_fill_manual(name = "Political Lean", 
                    labels = c("Liberal", "Conservative"),
                    values = c("Light Gray", "Dark Gray"))

>>>>

long_mlm$moraltype = factor(long_mlm$moraltype, 
                  levels=c("hperhi", "hperlo", "fperhi", "fperlo",
                           "iperhi", "iperlo", "aperhi", "aperlo", "pperhi", "pperlo"),
                  labels = c("Harm-positive", "Harm-negative", "Fair-positive",
                             "Fair-negative", "Ingroup-positive", "Ingroup-negative",
                             "Authority-positive", "Authority-negative", 
                             "Purity-positive", "Purity-negative")) 
cleanup = theme(panel.grid.major = element_blank(), 
                panel.grid.minor = element_blank(), 
                panel.background = element_blank(), 
                axis.line.x = element_line(color = "black"),
                axis.line.y = element_line(color = "black"),
                legend.key = element_rect(fill = "white"),
                text = element_text(size = 15))

long_mlm$moral_foundation = long_mlm$moraltype
long_mlm$moral_foundation = gsub("-positive", "", long_mlm$moral_foundation)
long_mlm$moral_foundation = gsub("-negative", "", long_mlm$moral_foundation)

long_mlm$valence = long_mlm$moraltype
long_mlm$valence = gsub("Harm-positive", "Positive", long_mlm$valence)
long_mlm$valence = gsub("Harm-negative", "Negative", long_mlm$valence)
long_mlm$valence = gsub("Authority-positive", "Positive", long_mlm$valence)
long_mlm$valence = gsub("Authority-negative", "Negative", long_mlm$valence)
long_mlm$valence = gsub("Fair-positive", "Positive", long_mlm$valence)
long_mlm$valence = gsub("Fair-negative", "Negative", long_mlm$valence)
long_mlm$valence = gsub("Purity-positive", "Positive", long_mlm$valence)
long_mlm$valence = gsub("Purity-negative", "Negative", long_mlm$valence)
long_mlm$valence = gsub("Ingroup-positive", "Positive", long_mlm$valence)
long_mlm$valence = gsub("Ingroup-negative", "Negative", long_mlm$valence)

overallgraph = ggplot(long_mlm, aes(moral_foundation, percent, fill = lean))
overallgraph +
  stat_summary(fun.y = mean,
               geom = "bar",
               position = "dodge") +
  stat_summary(fun.data = mean_cl_normal,
               geom = "errorbar", 
               position = position_dodge(width = 0.90),
               width = .2) +
  xlab("Moral Category") +
  ylab("Percent") + 
  cleanup +
  scale_fill_manual(name = "Political Lean", 
                    labels = c("Liberal", "Conservative"),
                    values = c("Light Gray", "Dark Gray")) +
  facet_grid(~valence) + 
  NULL
